Response to the defense feedback

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

We use the chi-square test to check if two leakage sites are independent. A chi-squared test can determine if there is a relationship between two categorical variables. Suppose we can summarize the data in a $r*c$  two-way contingency table. The chi-square test statistic and the degrees of freedom $v$ are calculated with the below formula:
\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k} \qquad	 v = (r - 1)(c - 1)\]
Here $O$ is the observed value, and $E$ is the expected value. A low value means that there is a high correlation between the two variables.

The null hypothesis is that the two leakages are independent.
We generate random inputs as the secret and record the memory access for each execution. For each time, the execution is independent of the previous execution. The times of the same observation for each event should satisfy the normal distribution. After that, we can use the chi-squared test to test whether the two leakage sites are independent.

>>>>

We use the chi-squared test to check if two leakage sites are independent. A chi-squared test can determine if there is a relationship between two categorical variables. Suppose we can summarize the data in a $r*c$  two-way contingency table. The chi-squared test statistic and the degrees of freedom $v$ are calculated with the below formula:
\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k} \qquad	 v = (r - 1)(c - 1)\]
Here $O$ is the observed value, and $E$ is the expected value. A low value means that there is a high correlation between the two variables.

The null hypothesis is that the two leakages are independent.
We generate random inputs as the secret and record the memory access for each execution. For each time, the execution is independent of the previous execution. The times of the same observation for each event should satisfy the binomial distribution. After that, we can use the chi-squared test to test whether the two leakage sites are independent.
